Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-07-20 ms.tex
several minor edits

\begin{figure}
\begin{center}
\epsfig{file=tcomparison.eps, width=3.3in}
\caption{\label{fig:comparison} Comparison of SFD temperature, two-component 
model $T_2$, and \cite{planckdust} temperature (labeled $T_{R1.20}$) for a
 $10.5^{\circ}\times8.3^{\circ}$  region centered about 
$(l,b) = (111.6^{\circ}, 20.3^{\circ})$. Note the differing colorscales. Both 
models incorporating \PLANCK~data clearly show a major improvement in angular 
resolution relative to SFD.}
\end{center}
\end{figure}

@@

Lastly, during post burn-in sampling, we also estimate the monochromatic 
two-component intensity at 545 GHz, $M_{545}$ = $\langle M_{545, j} \rangle$ = 
$\langle \tilde{I}_{545, j}/b_{545}(T_{2,j}) \rangle$, its variance, and the 
545 GHz optical depth $\tau_{545}$=$\langle \tau_{545, j} \rangle$ = 
$\langle M_{545, j}/S_{545, j} \rangle$ and its variance. $\tau_{545}$ and 
$M_{545}$ are more readily useful than the sampling parameters themselves for 
translating our fit results into predictions of reddening ($\S$\ref{sec:ebv}) 
and thermal dust emission ($\S$\ref{sec:lofreq}), respectively.

@@

With $\bar{f}_1$=0.0485 (from Table \ref{tab:global}, model 2) and 
$\sigma_{\bar{f}_1}$=0.003. This is a fairly stringent prior, but we must 
restrict the fit from wandering with too much freedom, as we are attempting to 
constrain three parameters using an SED with only nine intensity measurements, 
several of which are quite noisy.

@@

% perhaps zodi will just magically be fixed in the forthcoming Planck dta
% release

%   ---> do i want a figure illustrating the CIBA problem at high latitude ?
%  ---> zodi
%  ---> more testing needed, in any event, to prove Planck based reddening
%       estimates outperform SFD

@@

% and should also say that it's worth looking up extinction values here
% to gauge whether results are dependent on choice of dust map

>>>>

\begin{figure}
\begin{center}
\epsfig{file=tcomparison.eps, width=3.3in}
\caption{\label{fig:comparison} Comparison of SFD temperature, two-component 
model $T_2$, and \cite{planckdust} temperature (labeled $T_{R1.20}$) for a
 $10.5^{\circ}\times8.3^{\circ}$  region centered about 
$(l,b) = (111.6^{\circ}, 18.3^{\circ})$. Note the differing colorscales. Both 
models incorporating \PLANCK~data clearly show a major improvement in angular 
resolution relative to SFD.}
\end{center}
\end{figure}

@@

Lastly, during post burn-in sampling, we also estimate the monochromatic 
two-component intensity at 545 GHz, $M_{545}$ = $\langle M_{545, j} \rangle$ = 
$\langle \tilde{I}_{545, j}/b_{545}(T_{2,j}) \rangle$, its variance, and the 
545 GHz optical depth $\tau_{545}$=$\langle \tau_{545, j} \rangle$ = 
$\langle M_{545, j}/S_{545, j} \rangle$ and its variance. $\tau_{545}$ and 
$M_{545}$ are more readily useful than the sampling parameters themselves for 
translating our fit results into predictions of reddening ($\S$\ref{sec:ebv}) 
and thermal dust emission ($\S$\ref{sec:lofreq}), respectively. At high
Galactic latitude, we find a typical $T_2$ uncertainty of 0.45 K, and
typical $\tilde{I}_{545}$ fractional uncertainty of 13\%.

@@

With $\bar{f}_1$=0.0485 (from Table \ref{tab:global}, model 2) and 
$\sigma_{\bar{f}_1}$=0.005. This is a fairly stringent prior, but we must 
restrict the fit from wandering with too much freedom, as we are attempting to 
constrain three parameters using an SED with only nine intensity measurements, 
several of which are quite noisy.

@@

% perhaps zodi will just magically be fixed in the forthcoming Planck
%   ---> do i want a figure illustrating the CIBA problem at high latitude ?
%  ---> zodi
%  ---> more testing needed, in any event, to prove Planck based reddening
%       estimates outperform SFD

@@
